\subsection{Brandon Chatham}
Fall 3\\
Next week we plan on meeting with Dr. Fern to talk over our drafted problem statement. We did our best to write it this week with what we had gathered from our first meeting with him about what he imagines the project being. Hopefully, what we have is in-line with what he wants and he will sign-off on it.\\ This week we did some research on what is required for our competing in the Starcraft AI competition. We also started looking at some other agents created by other universities to see what other people have done. I familiarized myself with the BWAPI and did some research on what the benefits of our creating a sandbox for our project will be and why it was necessary. Sandbox development is a pretty basic and fundamental component to our project that I really had no familiarity with so I wanted to make sure I caught myself up to speed in that respect.\\ Our primary problem was Dr. Fern being out of the office this week, but that was not a big issue. Also, I still need to learn LaTeX which is not exactly a problem, but something I need to focus on. I had an issue trying to mess around with the BWAPI this week because in order to use it, I need to install a version of Stacraft Brood War which costs 15 dollars. I figured Dr. Fern might have a solution to that so I did not buy it, yet.\\
\\
Fall 4\\
This week we have been working on revising our problem statement and making sure it is up to par. Also, we met with all of our advising sources to sort out what those revisions might be. Tomorrow, they will be completed.\\ Next week we will start working on our next document. I need to start looking into the IEEE standard and familiarize myself with those standards.\\ We had to meet with Prof. Fern a bit later than we had hoped because he was out, but we should be up to speed.\\
\\
Fall 5\\
We worked on revising our problem statement. Additionally, Kristen made a gantt chart for us and we pulled together our requirements document rough draft.\\ Next week we will meet with our client to talk over what our requirements document should have.\\ I had trouble balancing my coursework with a large project in Operating Systems due and trying to get myself organized for the career fair. Also, we had some issues getting our document signed by our client but we sorted that out.\\
\\
Fall 6\\
We received our feedback on the problem statement and will hopefully talk over how we can improve it soon. Kristen worked more on refining the requirements document after getting feedback from Prof. Fern on what he felt needed to be changed.\\ Next week we will meet on Tuesday, begin working on other documents, and potentially fine-tune our problem statement.\\ I had some trouble getting adjusted to the formatting expectations of the IEEE document specifications and am still getting used to LaTeX.\\
\\
Fall 7\\
Started planning our work for the Tech Review document and talking about what technologies we will be talking about.\\ Writing our Tech Review for Monday and beginning to familiarize ourselves with the resources we will be working with for the project.\\ Not many problems other than two of our team members being sick but we have been able to keep up with the workload.\\
\\
Fall 8\\
We finished our work on the Tech Review.\\ Meet with group to start talking about our final project presentation and the design doc.\\ Trying to wrap my head around the IEEE format for the design doc and how I'll apply what I am focusing on for the project.\\
\\
Fall 9\\
Got feedback on our work for the Tech Review. We were not exactly thrilled with our overall grade but we plan to make some good revisions.\\ Meet with team to talk about our upcoming work for final presentation, design doc, and the tech review revisions.\\ Still trying to make sure I'm correctly understanding what is exactly expected for this next doc.\\
\\
Fall 10\\
Worked on and completed my design document portion.\\ Trying to find a way to work around Kristen's unfortunate family situation to get our final presentation done.\\
\\
Winter 1\\
I set up my machine with Starcraft Broodwar and BWAPI. I started fiddling around with some of the example modules and familiarized myself with how to start running the AI modules on our local machines.\\ Start writing code for the resource module which will allow us to start expanding into other modules once we have resources to spend.\\ Having some difficulties finding times for our group to meet and struggling to balance school with many job applications.\\
\\
Winter 2\\
Met with the team and started talking about our individual development schedules.\\ Writing code and pushing to our repository.\\ Same as last week\\
\\
Winter 3\\
Started getting development organized and got to the "starting line" for writing code and wrote code this week which we pushed.\\ Continue working on modules and utilizing them in our AI module. The resource module is nearly complete with basic functions to get the AI started. We will need to develop more sophisticated logic behind optimizing resource gathering in order to best suit our strategy and really, and economic desires. (The more resources the better in all scenarios as any improvements should improve every possible strategy.)\\ None\\
\\
Spring 1\\
Worked on the scraper implementation.\\ Talk with Kristen about the documentation for the scraper.\\ None.\\
\\
Spring 2\\
Worked on the scouting class a bit.\\ Work with the team on deciding our poster layout.\\ Finding time to meet with our client.\\
\\
Spring 3\\
Working on finalizing our project and making sure our expectations are met.\\ Meet with client and fix any minor bugs.\\ One persistent bug in our resource gathering class.\\
\\
Spring 4\\
Fixing the expansion bug.\\ Bring in a replay processor for our data mining.\\ None.\\
\\
Spring 5\\
Still need to fix the expansion bug.\\ Get our midterm report done and our pitch ready.\\ None.\\
\\
Spring 6\\
Tried to fix the expansion bug but were not able to.\\ Get our midterm report done and our pitch ready.\\ Couldn't fix the bug.\\
\\
Spring 7\\
If you were to redo the project from Fall term, what would you tell yourself?\\
To pay more attention to machine learning neural networks and how to fit that into the project.\\
\\
What's the biggest skill you've learned?\\
I have developed my skill to teach myself new technologies outside of the classroom setting which will be invaluable in the workplace setting.\\
\\
What skills do you see yourself using in the future?\\
My ability to convey my technical ideas and skills as well as my further-developed self learning skills.\\
\\
What did you like about the project, and what did you not?\\
I did not love how little guidance we received from our client but I did enjoy being able to learn through trial and error. Also finding ways to fix our mistakes once we realized we had made them.\\
\\
What did you learn from your teammates?\\
A lot about technical skills and how to best work together on such a large project.
\\
If you were the client for this project, would you be satisfied with the work done?\\
The package we developed is pretty decent and I think it could be a good starting point for new developers in the AI club he plans to start.\\
\\
If your project were to be continued next year, what do you think needs to be working on?\\
Definitely implementing neural networks that make our AI more dynamic. As is, we have created an interface to interact with it, but the neural network would take our project to the next level.\\
\\
Speak a little about your expo experience.\\
Expo was probably my least favorite part of the capstone project. While it was fun explaining the project to interested people, it was a bit of an elongated event in my opinion.